---
title: "Are Legal Inequalities Being Improved WorldWide in the Past Fifty Years?"
subtitle: " A Replication of the Paper 'Gendered Laws and Women in the Workforce'."
author: 
  - Fan Yang
thanks: "Code and data are available at https://github.com/FanYang111/Replication-Paper and the social science reproduction platform link is https://www.socialsciencereproduction.org/reproductions/ab0f90ba-6bc6-451e-a695-52e1402f6d7f/index."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Gender inequality is a very common social problem. This paper replicates 'Gendered Laws and Women in the Workforce'(Hyland, Djankov and Goldberg). We find that although legal equality has improved dramatically over the past 50 years, women still enjoy far less power than men in some regions. Furthermore, we find that women's rights are linked to regional stability and economic development. And more equal laws help build a more equal labour market."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: reference.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(ggplot2)
library(stringr)
library(PMCMRplus)
library(kableExtra)
```

```{r,include=FALSE}
data=read.csv("data.csv")
```

#  Introduction

Gender inequality has long been an issue of great concern to society. One of the most visible manifestations of this is the unequal treatment of gender in the law. Most of the research into this problem has been carried out in individual countries. While it has been rarely studied from a global perspective.
 
Hyland, Djankov and Goldberg’s paper “Gendered Laws and Women in the Workforce” studies the gender discrimination by law in a global view for the first time. And the paper also looks at how legal inequality for women have changed over the last 50 years. The data used in the paper is Women, Business and the Law (WBL) data collected by the World Bank. The paper suggests that more equals laws about women labor force tend to constitute a more equal labor market.

This paper is a replication of the paper “Gendered Laws and Women in the Workforce”. We first discuss the WBL data in the data section and plot the changes in legal inequality for women in the past 50 years. In the result section, we check some of the findings of the original paper. Moreover, we are also interested in whether income is linked to the WBL index. Does the lower the income the lower the WBL index? Last but not the least, in the discussion part, we discuss some of our findings through the paper as well as the limitations and weaknesses of our paper.

#  Original Paper

This paper is a replication of the paper "Gendered Laws and Women in the Workforce". In the original paper, the authors Hyland, Djankov and Goldberg used the Women, Business and Law data from the world bank and analyzed the legal inequality between men and women from a global perspective for the first time. The findings of the paper are listed below:

  1) In 2019, women worldwide had about three-quarters of rights of men on average. 
  2) Women have the lowest treatment in laws and regulations of payment and parenthood.
  3) Women's treatment has improved over the past 50 years, but the rate of improvement varies by region.
  4) The pace of reform varies by country and by indicator.
  5) Legal equality and women's treatment in the labor market are positively correlated.
  
#  Data

This paper uses Rstudio(@citationr) to analyze. Package knitr(@citationknitr) and kableExtra (@citationkableExtra) is used to make tables and package ggplot2(@citationggplot2) is used to generate figures for the paper. We use the package tidyr(@citationtidyr) to separate the variable generated in the for loop and the package PMCMRplus(@citationPMCMRplus) to conduct the One-Way ANOVA test.

##  Women, Business and Law (WBL) Data

The WBL data is collected by the World Bank since 1970. The data collects the laws and regulations that can affect women’s opportunities in the labor market in 190 economies. The aim of the data is to provide data for researchers to study the gender inequality in economic opportunities and empowerment, thus leading to a world of gender equality.

## Variables of the WBL Data

There are a total number of 50 variables in the data, our main focus is the following 11 variables:

1. Region. Region is  the area in which an economy is located. It is divided into 7 sections, which are South Asia, Sub-Saharan Africa, Europe and Central Asia, Middle East and North Africa, Latin America and Caribbean, High income: OECD, East Asia and Pacific.
2. WBL INDEX. The WBL index is the measure of the percentage of legal equality between men and women in one economy. This is our main outcome of interest as it indicates the legal rights of women.
3. Income Group. The income group is divided into four parts, which are Low income, Lower middle income, Upper middle income and High income.

Variables 4 to 11 are the 8 variables that contribute to the WBL index. The questions below each variable are the laws and regulations that affect the variable. The score for each variable in each economy is determined by the answers to these questions. 

4. Mobility 
  1) Can a woman apply for a passport in the same way as a man?
  2) Can a woman travel outside the country in the same way as a man?
  3) Can a woman travel outside her home in the same way as a man?
  4) Can a woman choose where to live in the same way as a man?
  
5. Workplace 
  1) Can a woman get a job in the same way as a man?
  2) Does the law prohibit discrimination in employment based on gender?
  3) Is there legislation on sexual harassment in employment?
  4) Are there criminal penalties or civil remedies for sexual harassment in employment?
  
6. Pay
  1) Does the law mandate equal remuneration for work of equal value?
  2) Can women work the same night hours as men?
  3) Can women work in jobs deemed dangerous in the same way as men?
  4) Are women able to work in the same industries as men?
  
7. Marriage
  1) Can a woman be "head of household" or "head of family" in the same way as a man?
  2) Is there legislation specifically addressing domestic violence?
  3) Can a woman obtain a judgment of divorce in the same way as a man?
  4) Does a woman have the same rights to remarry as a man?
  
8. Parenthood
  1) Is paid leave of at least 14 weeks available to mothers?
  2) Does the government administer 100% of maternity leave benefits?
  3) Is there paid leave available to fathers?
  4) Is there paid parental leave?
  5) Is dismissal of pregnant workers prohibited?
  
9. Entrepreneurship
  1) Can a woman sign a contract in the same way as a man?
  2) Can a woman register a business in the same way as a man?
  3) Can a woman open a bank account in the same way as a man?
  4) Does the law prohibit discrimination in access to credit based on gender?
  
10. Asserts
  1) Do men and women have equal ownership rights to immovable property?
  2) Do sons and daughters have equal rights to inherit assets from their parents?
  3) Do female and male surviving spouses have equal rights to inherit assets?
  4) Does the law grant spouses equal administrative authority over assets during marriage?
  
11. Pension
  1) Are the ages at which men and women can retire with full pension benefits equal?
  2) Are the ages at which men and women can retire with partial pension benefits equal?
  3) Is the mandatory retirement age for men and women equal?
  4) Are periods of absence from work due to childcare accounted for in pension benefits?

## Data Ethics

We promise that all data in this article is from the World Bank's WBL data , which is reliable and has not been fabricated in any way. The data will only be used for the analysis of this article and will not be used by us for profit in any way.

## Analysis


### WBL INDEX

```{r,include=FALSE}
datac=c()
name=c()
year=c(1971, 1972, 1973 ,1974, 1975 ,1976, 1977 ,1978, 1979 ,1980, 1981, 1982, 1983, 1984, 1985, 1986, 1987 ,1988 ,1989 ,1990 ,1991, 1992, 1993 ,1994 ,1995, 1996 ,1997 ,1998 ,1999 ,2000, 2001 ,2002, 2003, 2004 ,2005, 2006, 2007 ,2008, 2009, 2010, 2011 ,2012 ,2013 ,2014 ,2015 ,2016, 2017, 2018 ,2019, 2020)
region=c("South Asia","Sub-Saharan Africa","Europe & Central Asia","Middle East & North Africa","Latin America & Caribbean","High income: OECD","East Asia & Pacific")
for(i in 1:7){
  for(j in 1:50){
  dat=data[which(data$Region==region[i]),]
  dat=dat[which(dat$WBL.Report.Year==year[j]),]
  datt=round(mean(dat$WBL.INDEX),2)
  name1=paste(region[i],",",year[j])
  datac=c(datac,datt)
  name=c(name,name1)
  }}
datac=as.data.frame(cbind(name,datac))
```

```{r,include=FALSE}
datac=separate(datac,col=name,into=c("Region","Year"),sep=",")
```

```{r,include=FALSE}
datt=data[which(data$WBL.Report.Year==2020),]
mean(datt$WBL.INDEX)
```

```{r Fig1,fig.width=6,fig.height=4, fig.cap="Average WBL Index of Different Region Over Time",echo=FALSE}
datac$Year=as.numeric(datac$Year)
datac$datac=as.numeric(datac$datac)
ggplot(data=datac,mapping=aes(x=Year,y=datac,group=Region,color=Region))+geom_line()+ylim(c(0,100))+xlab("Year")+ylab("WBL Index")+theme_minimal()
```

Figure \@ref(fig:Fig1) summarizes the average WBL index of different region in the past 50 years. In 1971, when the data was first gathered, the highest WBI index was Europe and Central Asia, which was 57.16. This means that in 1971, women in Europe and Central Asia were given 57.16% of the power that men were given in the areas covered by the index. This is closely followed by High income: OECD, with the WBL index 55.62. The region with the least women's right is Middle East and North Africa. The index was only 30.98.

We can see that the average WBL index is rising in all regions as time passes. The rise in the index is relatively smooth for areas High income: OECD, Latin America and Caribbean, East Asia and Pacific and Sub-Saharan Africa. However, for region Europe and Central Asia, South Asia and Middle East and North Africa, their indexes developed more slowly at first. The index for Europe and Central Asia even showed a decline in 1972 and 1981. The index increased quickly after 1995 for Europe and Central Asia.And the indexes for South Asia and Middle East and North Africa did not start rising fast until after 2000.

In 2020, the average WBL index is 75.25. The region with the highest index is High income: OECD, which is 94.66. This indicates that women and men in the region have approximately equal rights in law. The indexes for Europe and Central Asia and Latin America and Caribbean are higher than the average score. While the remaining four regions all have a score lower than the average. Among them, Middle East and North Africa gets the lowest score, which is only 49.57. 


### 8 Indicators

Figure \@ref(fig:Fig2) shows the changes in the eight indicators affecting the WBL index over the past 50 years. We find that all indices are increasing, indicating that women have been treated more equally by laws and regulations over time. Of these eight indicators, the most significant change is in workplace, which rose from less than 20 in 1970 to 78.42 in 2020, indicating a significant improvement in the treatment of women in the labour market.

Moreover, we find that although the score for workplace exceeds 75 in 2020, while the score for pay is only 66. This suggests that although the working opportunities for women are increasing, the income of women still needs to be improved.

```{r,include=FALSE}
data1=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$MOBILITY)
  name1=paste(year[i])
  data1=c(data1,datt)
  name=c(name,name1)
}
data1=cbind(name,data1)
Indicator=rep("Mobility",50)
data1=cbind(Indicator,data1)

data2=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$WORKPLACE)
  name1=paste(year[i])
  data2=c(data2,datt)
  name=c(name,name1)
}
data2=cbind(name,data2)
Indicator=rep("Workplace",50)
data2=cbind(Indicator,data2)

data3=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$PAY)
  name1=paste(year[i])
  data3=c(data3,datt)
  name=c(name,name1)
}
data3=cbind(name,data3)
Indicator=rep("PAY",50)
data3=cbind(Indicator,data3)

data4=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$MARRIAGE)
  name1=paste(year[i])
  data4=c(data4,datt)
  name=c(name,name1)
}
data4=cbind(name,data4)
Indicator=rep("Marriage",50)
data4=cbind(Indicator,data4)

data5=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$PARENTHOOD)
  name1=paste(year[i])
  data5=c(data5,datt)
  name=c(name,name1)
}
data5=cbind(name,data5)
Indicator=rep("Parenthood",50)
data5=cbind(Indicator,data5)

data6=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$ENTREPRENEURSHIP)
  name1=paste(year[i])
  data6=c(data6,datt)
  name=c(name,name1)
}
data6=cbind(name,data6)
Indicator=rep("Entrepreneurship",50)
data6=cbind(Indicator,data6)

data7=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$ASSETS)
  name1=paste(year[i])
  data7=c(data7,datt)
  name=c(name,name1)
}
data7=cbind(name,data7)
Indicator=rep("Asserts",50)
data7=cbind(Indicator,data7)

data8=c()
name=c()
for(i in 1:50){
  dat=data[which(data$WBL.Report.Year==year[i]),]
  datt=mean(dat$PENSION)
  name1=paste(year[i])
  data8=c(data8,datt)
  name=c(name,name1)
}
data8=cbind(name,data8)
Indicator=rep("Pension",50)
data8=cbind(Indicator,data8)

datt1=as.data.frame(rbind(data1,data2,data3,data4,data5,data6,data7,data8))
```


```{r Fig2, fig.width=6, fig.height=4,fig.cap= "Charting the Progress of the Indicators over Time",echo=FALSE}
datt1$name=as.numeric(datt1$name)
datt1$data1=as.numeric(datt1$data1)
ggplot(data=datt1,mapping=aes(x=name,y=data1,group=Indicator,color=Indicator))+geom_line()+ylim(c(0,100))+xlab("Year")+ylab("Score")+theme_minimal()
```



```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data1=c()
data1sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$MOBILITY),2)
  d2=round(sd(datt$MOBILITY),2)
  data1=c(data1,d1)
  data1sd=c(data1sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data1=cbind(name,data1)
data1sd=cbind(name,data1sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data2=c()
data2sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$WORKPLACE),2)
  d2=round(sd(datt$WORKPLACE),2)
  data2=c(data2,d1)
  data2sd=c(data2sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data2=cbind(name,data2)
data2sd=cbind(name,data2sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data3=c()
data3sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$PAY),2)
  d2=round(sd(datt$PAY),2)
  data3=c(data3,d1)
  data3sd=c(data3sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data3=cbind(name,data3)
data3sd=cbind(name,data3sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data4=c()
data4sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$MARRIAGE),2)
  d2=round(sd(datt$MARRIAGE),2)
  data4=c(data4,d1)
  data4sd=c(data4sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data4=cbind(name,data4)
data4sd=cbind(name,data4sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data5=c()
data5sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$PARENTHOOD),2)
  d2=round(sd(datt$PARENTHOOD),2)
  data5=c(data5,d1)
  data5sd=c(data5sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data5=cbind(name,data5)
data5sd=cbind(name,data5sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data6=c()
data6sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$ENTREPRENEURSHIP),2)
  d2=round(sd(datt$ENTREPRENEURSHIP),2)
  data6=c(data6,d1)
  data6sd=c(data6sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data6=cbind(name,data6)
data6sd=cbind(name,data6sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data7=c()
data7sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$ASSETS),2)
  d2=round(sd(datt$ASSETS),2)
  data7=c(data7,d1)
  data7sd=c(data7sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data7=cbind(name,data7)
data7sd=cbind(name,data7sd)
```

```{r,include=FALSE}
dat=data[which(data$WBL.Report.Year==2020),]
data8=c()
data8sd=c()
name=c()
for(i in 1:7){
  datt=dat[which(dat$Region==region[i]),]
  d1=round(mean(datt$PENSION),2)
  d2=round(sd(datt$PENSION),2)
  data8=c(data8,d1)
  data8sd=c(data8sd,d2)
  name1=paste(region[i])
  name=c(name,name1)
}
data8=cbind(name,data8)
data8sd=cbind(name,data8sd)
```

```{r,include=FALSE}
data1=cbind(data1,data1sd)
data2=cbind(data2,data2sd)
data3=cbind(data3,data3sd)
data4=cbind(data4,data4sd)
data5=cbind(data5,data5sd)
data6=cbind(data6,data6sd)
data7=cbind(data7,data7sd)
data8=cbind(data8,data8sd)
```

```{r,include=FALSE}
d1=as.data.frame(cbind(data1,data2,data3,data4,data5,data6,data7,data8))
d1=d1[,c(1,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32)]
d1$Mobility=str_c(d1$data1,",",d1$data1sd)
d1$Workplace=str_c(d1$data2,",",d1$data2sd)
d1$Pay=str_c(d1$data3,",",d1$data3sd)
d1$Marriage=str_c(d1$data4,",",d1$data4sd)
d1$Parenthood=str_c(d1$data5,",",d1$data5sd)
d1$Entrepreneurship=str_c(d1$data6,",",d1$data6sd)
d1$Assets=str_c(d1$data7,",",d1$data7sd)
d1$Pension=str_c(d1$data8,",",d1$data8sd)
d1=d1[,c(1,18:25)]
names(d1)[1]="Region"

da=read.csv("d1.csv")
da=da[,(2:10)]
```

We also calculated the average score for 8 indicators in different regions in 2019. Table 1 summarizes the 2019 averages for the eight indicators across different regions. High-income: OECD has the highest scores in Mobility, Workplace, Pay, Parenthood, Entrepreneurship and pension. Moreover, the standard deviation of all 8 indicators are small in the region. This suggests that laws and regulations for women do not vary much across countries in the region. 

The highest score in Assets and Marriage is Europe and Central Asia. While the region performs badly in Pay and Pension. The score for Pay is 66 and the score for Pension is only 54, indicating that women enjoy far less rights than men in these two areas in Europe and Central Asia.

Meanwhile, we find that women in Middle East and North Africa had the least rights. The scores for Mobility, Workplace, Pay, Marriage, Parenthood, Assets and Pension are all below 60.

```{r,echo=FALSE}
kable(da, booktabs = TRUE,caption = "Average regional score in 2019 for each WBL indicator") %>%
  kable_styling(font_size = 6)
```


#  Results

## Findings of Original Paper

In 2019, the average WBL index worldwide is 75.26. This suggests that in 2019, women around the world had an average of 75.26% of the power of men, which is associated with the first finding of the original paper.

We also find that women were treated worst in pay and parenthood. Figure \@ref(fig:Fig2) suggests that starting from 1970, the average scores for pay and parenthood were in the last three. In year 1996, the score for workplace exceeded the score for parenthood. After this, the score in parenthood have been at the bottom. And in 2004, the score for workplace exceeded the score for pay. And it has become the second lowest score after that. Till 2019, the score for pay is only 66 and the score for parenthood is only 53.89. Therefore, the second finding of the original paper is correct. Women are treated most unequal in laws and regulations of pay and parenthood.

The third finding of the original paper is also supported. Figure \@ref(fig:Fig1) shows that till 2020, women in the Middle East and North Africa region enjoy less than 50% of the power of men. While in High income: OECD, women's rights are 94.66% of men. This may be related to the economic development and stability of the region. The Middle East and North Africa is perennially in conflict. And the North Africa is particularly underdeveloped.

Moreover, we find that the development speed of different indicators is not the same. The fastest growing is the workplace. In 50 years of development, its score has grown by about 440%. It was followed by parenthood, whose score rose from 17.16 to 53.89. For the remaining indicators, their development is relatively flat, and there is no doubling of growth. 

Figure \@ref(fig:Fig4) plots the scatterplot of WBL index and the scores for pay based on income groups. The vast majority of those who score full marks for pay and have a WBL score of 80 or more are high income and upper middle income. Most of those who scored 0 in pay are low income or lower middle income economies. Also, we fit best fitted lines according to the different groups. We find that they are all positively correlated, indicating that the higher the pay score the higher the WBL index. 

Figure \@ref(fig:Fig5) plots the scatterplot of WBL index and the scores for workplace based on income groups. Besides score 0 in workplace, the highes WBL index for all other scores is high income. Also, the slopes of best fitted lines of all four income groups are positive, suggesting that the higher the workplace score, the higher the WBL index.

Therefore, we make the conclusion that the fith finding of the original paper is correct. That is, legal equality is positive correlated to the equality in labor force market.

## Income and WBL Index
```{r Fig3,fig.width=6,fig.height=4,fig.cap="Income Group and WBL Index",echo=FALSE,warning=FALSE}
ggplot(data=data,mapping=aes(x=data$Income.group,y=data$WBL.INDEX,group=data$Income.group,color=data$Income.group))+geom_boxplot()+ylim(c(0,100))+xlab("Group")+ylab("WBL Index")+theme_minimal()+
  scale_colour_discrete("Income Group")+theme(axis.text = element_text(size = 7))  
```

Figure \@ref(fig:Fig3) plots the WBL index based on income group of the economy. We find that the average WBL index is highest for High income economies, followed by Upper middle income, lower middle income and low income. The smallest difference between WBL index is in the low income economies. For high income economies, it has the widest range. It not only has economies with full index, but also has economies with the lowest index of just 17.5. Moreover, we find that the range of economies in upper middle income is also very broad. 

To test whether the WBL index is related to income, we use one way anova to compare the differences between groups. Package stats is used here to conduct the anova test. Table 2 summarizes the output of the test. We find differences in the mean WBL index between each of the two groups. The biggest difference is between the high income and the low income. The p-values for all group comparisons are smaller than 0.05, suggesting that all the pairs are statistically significant. Therefore, we make the conclusion that the income group is a factor that affects WBL Index. When other factors are not taken into account, we predict a WBL index of 68 for high income economies, 59.55 for upper middle income economies, 53.68 for lower middle income economies and 49.56 for low income economies.

```{r,echo=FALSE}
fit=aov(data$WBL.INDEX~data$Income.group,data=data)
res=TukeyHSD(fit, conf.level = 0.95)
d1=as.data.frame(res$`data$Income.group`)
names(d1)=c("Mean Difference","Lower Quantile","Upper Quantile","P-Value Adjusted")
kable(d1, booktabs = TRUE,caption = "One Way ANOVA of Income Group and WBL Index") %>%
  kable_styling(font_size = 8)
```

```{r,include=FALSE}
m1=lm(data$WBL.INDEX~data$Income.group,data=data)
m1$coefficients
```

# Discussion

## Regional stability and economic development are important factors in enhancing legal equality.

Region with the highest WBL index is high income: OECD. The countries in this region are developed countries. They have a high per capita gdp and a developed infrastructure. At the same time, these countries have experienced many years of peaceful development. In contrast, most of the countries in the Middle East and North Africa, the region with the lowest WBL index, are developing or underdeveloped countries, and many of these countries are constantly at war. Therefore, we make the conclusion that regional stability and economic development are important factors in enhancing legal equality.

## Equal treatment in laws and regulations is progressing, but still need more focus on regulations and laws on family and wages.

We find that all eight indicators included in the WBL database have improved significantly over the last 50 years, but the averages for income and parenthood are still at the bottom. Women in the Middle East and North Africa and South Asia have the least power in both areas. For other regions, with the exception of high income: OECD, women have less than 70% of the power compared with men in terms of laws and regulations on pay. And for parenthood, except for high income: OECD and Europe and Central Asia, the average score is below 50% in all other regions. Therefore, we can see that all countries should strengthen laws and regulations on women's income and family, so that women can be treated more equally in these two areas.

## Income is an unignorable fact of WBL index. 

The one way ANOVA test suggests that there exists great difference between each income group. In general, high-income economies have relatively high WBL index. Although there are individual high incomes where the WBL index is lower than the average for low incomes, we conclude that higher incomes correspond to higher wbl indices. Although there are individual high incomes where the WBL index is lower than the average for low incomes, we conclude that higher incomes correspond to higher WBL index.

## Weakness and Improvements

There are still large differences in income between provinces of the country, so we cannot determine the WBL index solely from income gradations. For example, the coastal provinces of China, such as Jiangsu, Shanghai and Guangzhou, all have high incomes. Women enjoy relatively more equal laws and regulations in these provinces In contrast, some inland provinces, with lower incomes and lower levels of female education, should have a lower WBL index for women than in coastal areas. To improve this, we can divide the different provinces of the country by GDP, rather than generally assigning the country to a certain income group.

In addition, this paper examines the difference between legal equality for men and women in terms of income and workplace through descriptive analysis only. To improvement the reliability, linear models should be built to analyze the correlation.


\newpage

# Appendix

## 

```{r Fig4,fig.cap="Pay and WBL Index of Different Income Groups",message=FALSE,echo=FALSE,warning=FALSE}
ggplot(data=data,mapping=aes(x=data$PAY,y=data$WBL.INDEX,color=data$Income.group))+geom_point()+xlab("PAY")+ylab("WBL Index")+theme_minimal()+
  scale_colour_discrete("Income Group")+
     geom_smooth(method = "lm", se = FALSE)
```

```{r Fig5,fig.cap="Workplace and WBL Index of Different Income Groups",echo=FALSE,message=FALSE,warning=FALSE}
ggplot(data=data,mapping=aes(x=data$WORKPLACE,y=data$WBL.INDEX,color=data$Income.group))+geom_point()+xlab("Workplace")+ylab("WBL Index")+theme_minimal()+
  scale_colour_discrete("Income Group")+
     geom_smooth(method = "lm", se = FALSE)
```


\newpage

# References
